---
title: "mics analysis"
format: pdf
keep-tex: true
---

## Ordinal

```{r}
#| label: library
#| echo: false
#| message: false
#| warning: false
#| eval: false

library(gt)
library(gtsummary)
library(tidyverse)
library(haven)
library(foreign)
library(sjPlot)
library(kableExtra)
```

```{r}
#| label: ordinal-sum-tab
#| echo: false
#| message: false
#| warning: false
#| eval: false

load("ordinal_sum_tab.Rdata")
ordinal_sum_tab
```

```{r}
#| label: ordinal-mod-full
#| echo: false
#| message: false
#| warning: false
#| eval: false


load("ordinal_model_sum.Rdata")
ordinal_model_sum |> 
  mutate(p.value = if_else(p.value < 0.01, "<0.01", 
                           as.character(round(p.value, 2)))) |> 
  kable(
    digits = 2, 
    escape = FALSE, 
    format = "latex", 
    booktabs = TRUE
  )
```

\newpage

```{r}
#| label: multinom-summary-tab
#| echo: false
#| message: false
#| warning: false
#| eval: false

load("multinom_summary_tab.Rdata")
multinom_summary_tab

```

```{r}
#| label: multinom-mod-full-govt
#| echo: false
#| message: false
#| warning: false
#| eval: false

load("mod1_summ.Rdata")
mod1_summ |> 
  as_tibble() |> 
  select(term, estimate, conf.low, conf.high, p.value) |> 
  mutate(
    estimate = exp(estimate),
    conf.low = exp(conf.low),
    conf.high = exp(conf.high),
    p.value = if_else(p.value < 0.01, "<0.01", 
                           as.character(round(p.value, 2)))) |> 
  kable(
    digits = 2, 
    escape = FALSE, 
    format = "latex", 
    booktabs = TRUE,
    caption = "Multinom Model Govt"
  )

```

```{r}
#| label: multinom-mod-full-private
#| echo: false
#| message: false
#| warning: false
#| eval: false

load("mod2_summ.Rdata")
mod2_summ |> 
  as_tibble() |> 
  select(term, estimate, conf.low, conf.high, p.value) |> 
  mutate(
    estimate = exp(estimate),
    conf.low = exp(conf.low),
    conf.high = exp(conf.high),
    p.value = if_else(p.value < 0.01, "<0.01", 
                           as.character(round(p.value, 2)))) |> 
  kable(
    digits = 2, 
    escape = FALSE, 
    format = "latex", 
    booktabs = TRUE,
    caption = "Multinom Model Private"
  )

```

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 11\tabcolsep) * \real{0.2304}}
  >{\centering\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1667}}
  >{\centering\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1667}}
  >{\centering\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.2292}}
  >{\centering\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.0903}}@{}}
\caption{Summary Table of Different Characteristics for Ordinal Model} \\
\label{tab:summary_ordinal} \\
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Characteristic}
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
\textbf{Overall}, \\ N = 21,705
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
\textbf{Stunted}, \\ N = 4,241
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
\textbf{Severely Stunted}, \\ N = 1,801
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
\textbf{Pvalue}
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
\textbf{Child Age} & & & & \textless0.001 \\
 \quad \textless1 Year & 4,201 (100\%) & 497 (12\%) & 221
(5.3\%) & \\
 \quad 1-3 Years & 8,946 (100\%) & 1,982 (22\%) & 902 (10\%)
& \\
\quad 3-5 Years & 8,558 (100\%) & 1,762 (21\%) & 678 (7.9\%)
& \\
\textbf{Division} & & & & \textless0.001 \\
\quad Barishal & 1,970 (100\%) & 396 (20\%) & 173 (8.8\%) & \\
\quad Chattogram & 4,451 (100\%) & 848 (19\%) & 392 (8.8\%)
& \\
\quad Dhaka & 4,246 (100\%) & 784 (18\%) & 349 (8.2\%) & \\
\quad Khulna & 3,051 (100\%) & 528 (17\%) & 129 (4.2\%) & \\
\quad Mymenshing & 1,310 (100\%) & 309 (24\%) & 127 (9.7\%) & \\
\quad Rajshahi & 2,304 (100\%) & 448 (19\%) & 157 (6.8\%) & \\
\quad Rangpur & 2,546 (100\%) & 463 (18\%) & 250 (9.8\%) & \\
\quad Sylhet & 1,827 (100\%) & 465 (25\%) & 224 (12\%) & \\
\textbf{Sex} & & & & 0.6 \\
\quad Male & 11,195(100\%) & 2,195 (20\%) & 948 (8.5\%) & \\
\quad Female & 10,510(100\%) & 2,046 (19\%) & 853 (8.1\%) & \\
\textbf{Area} & & & & \textless0.001 \\
\quad Urban & 3,941(100\%) & 688 (17\%) & 282 (7.2\%) & \\
\quad Rural & 17,764(100\%) & 3,553 (20\%) & 1,519 (8.6\%)
& \\
\textbf{Wealth Index} & & & & \textless0.001 \\
\quad Poorest & 5,382 (100\%) & 1,384 (26\%) & 645 (12\%) & \\
\quad Second & 4,578 (100\%) & 1,002 (22\%) & 409 (8.9\%) & \\
\quad Middle & 4,144 (100\%) & 765 (18\%) & 292 (7.0\%) & \\
\quad Fourth & 4,075 (100\%) & 659 (16\%) & 251 (6.2\%) & \\
\quad Richest & 3,526 (100\%) & 431 (12\%) & 204 (5.8\%) & \\
\textbf{Education Level} & & & & \textless0.001 \\
\quad None & 2,422 (100\%) & 648 (27\%) & 318 (13\%) & \\
\quad Primary & 5,253 (100\%) & 1,207 (23\%) & 574 (11\%) & \\
\quad Secondary & 10,706(100\%) & 1,940 (18\%) & 737 (6.9\%)
& \\
\quad Higher & 3,324 (100\%) & 446 (13\%) & 172 (5.2\%) & \\
\textbf{BMI} & 14.95 (14.03, 16.03) & 14.84
(14.03, 15.86) & 15.27 (14.27, 16.82) & \textless0.001 \\
\end{longtable}

\newpage

![Distribution of Stunting Over Disitricts](../ordinal_plot_districts.pdf)

\newpage 

\begin{table}[h!]
\centering
\caption{Odds Ratio and 95\% CI of Different Variables for Ordinal Model}
\label{tab:model_ordinal}
\begin{tabular}{lrrrl}
\toprule
\textbf{Variable} & \textbf{Odds Ratio} & \textbf{Conf. Low} & \textbf{Conf. High} & \textbf{Pvalue}\\
\midrule
\textbf{Child Age} & & & & \\
(\textbf{ref: <1 Year}) \\
\quad 1-3 Years & 2.59 & 2.36 & 2.85 & <0.01\\
\quad 3-5 Years & 2.36 & 2.14 & 2.61 & <0.01\\
\addlinespace
\textbf{Division} & & & & \\
(\textbf{ref: Barisal}) \\
\quad Chattogram & 1.15 & 0.89 & 1.49 & 0.28\\
\quad Dhaka & 1.08 & 0.84 & 1.39 & 0.54\\
\quad Khulna & 0.83 & 0.63 & 1.08 & 0.16\\
\quad Mymenshing & 1.22 & 0.88 & 1.69 & 0.22\\
\quad Rajshahi & 1.02 & 0.77 & 1.34 & 0.91\\
\quad Rangpur & 1.05 & 0.80 & 1.38 & 0.74\\
\quad Sylhet & 1.77 & 1.29 & 2.44 & <0.01\\
\addlinespace
\textbf{Place Of Residence} & & & & \\
(\textbf{ref: Urban}) \\
\quad Rural & 0.94 & 0.86 & 1.03 & 0.21\\
\addlinespace
\textbf{Wealth Index} & & & & \\
(\textbf{ref: Poorest}) \\
\quad Second & 0.80 & 0.73 & 0.87 & <0.01\\
\quad Middle & 0.63 & 0.57 & 0.69 & <0.01\\
\quad Fourth & 0.53 & 0.48 & 0.59 & <0.01\\
\quad Richest & 0.35 & 0.31 & 0.40 & <0.01\\
\addlinespace
\textbf{Education Level} & & & & \\
(\textbf{ref: None}) \\
\quad Primary & 0.87 & 0.79 & 0.96 & <0.01\\
\quad Secondary & 0.68 & 0.62 & 0.75 & <0.01\\
\quad Higher & 0.58 & 0.51 & 0.66 & <0.01\\
\addlinespace
\textbf{BMI} & 1.16 & 1.14 & 1.19 & <0.01\\
\addlinespace
\hline
\textbf{Thresholds} & \textbf{Estimates (log)} & & & \\
\quad Normal|Stunted & 3.38 & 2.95 & 3.82 & <0.01\\
\quad Stunted|Severely Stunted & 4.91 & 4.48 & 5.33 & <0.01\\
\addlinespace
\hline
\textbf{Random Effect} & \textbf{Estimates} & & & \\
\quad Districts(HH7A) & 0.25 & & & \\
\quad ICC & 0.02 & & & \\
\bottomrule
\end{tabular}
\end{table}

\newpage

\begin{table}[htbp]
\centering
\caption{Comparison of MOR Between Null and Covariate-Adjusted Ordinal Models}
\label{tab:mor_comparison_ord}
\begin{tabular}{@{}lcccc@{}}
\toprule
 & \multicolumn{2}{c}{\textbf{Null Models\footnote{Null Models: This model does not include any covariates.}}} & \multicolumn{2}{c}{\textbf{Covariate-Adjusted Models}} \\
 \cmidrule(lr){2-3} \cmidrule(lr){4-5}
Term & Estimates & 95\% CI & Estimates & 95\% CI \\ 
\midrule
$\widehat{\mbox{MOR}_{stunted}}$ & 1.34 & (1.27, 1.44) & 1.24 & (1.19, 1.31) \\
\bottomrule
\end{tabular}
\scriptsize
\text{Null Models: This model does not include any covariates}
\end{table}

\newpage

## Multinomial models

\newpage

\begin{table}
\centering
\caption{Summary Table of Characteristics for Multinomial Model}
\label{tab:summary_multinom}
\begin{tabular}{@{}p{0.30\textwidth}p{0.2\textwidth}p{0.15\textwidth}p{0.2\textwidth}p{0.1\textwidth}@{}}
\toprule
\textbf{Characteristic} & \textbf{Sample \ } $N$=3,769 & \textbf{Govt(\%)} $N$=618 & \textbf{Private(\%)} $N$=2,110 & \textbf{P-value} \\
\midrule
\textbf{Education Level} & & & & 0.008 \\
\quad None & 278 & 17.63 & 50.36 & \\
\quad Primary & 918 & 16.99 & 54.79 & \\
\quad Secondary & 1,959 & 15.82) & 55.54 & \\
\quad Higher & 614 & 16.78 & 61.73 & \\
\textbf{Area} & & & & <0.001 \\
\quad Urban & 739 & 21.38 & 64.82 & \\
\quad Rural & 3,030 & 15.18 & 53.83 & \\
\textbf{Wealth Index} & & & & <0.001 \\
\quad Poorest & 883 & 18.23 & 48.13 & \\
\quad Second & 782 & 15.35 & 48.08 & \\
\quad Middle & 729 & 16.19 & 54.32 & \\
\quad Fourth & 754 & 15.92 & 61.41 & \\
\quad Richest & 621 & 15.94 & 72.46 & \\
\textbf{Division} & & & & <0.001 \\
\quad Barishal & 382 & 17.54 & 53.14 & \\
\quad Chattogram & 871 & 10.79 & 65.67 & \\
\quad Dhaka & 687 & 17.76 & 66.67 & \\
\quad Khulna & 568 & 18.49 & 41.02 & \\
\quad Mymenshing & 199 & 29.15 & 45.73 & \\
\quad Rajshahi & 403 & 19.85 & 55.83 & \\
\quad Rangpur & 419 & 13.84 & 41.53 & \\
\quad Sylhet & 240 & 14.17 & 64.17 & \\
\bottomrule
\end{tabular}
\end{table}

\newpage

\begin{table}
\caption{\label{tab:multinom-mod-full-govt}Multinom Model Govt}
\centering
\begin{tabular}[t]{lrrrl}
\toprule
\textbf{Variable} & \textbf{Odds Ratio} & \textbf{Conf. Low} & \textbf{Conf. High} & \textbf{Pvalue}\\
\midrule
\addlinespace
& & \textbf{Base(Informal)} & & \\
\addlinespace
Intercept & 1.48 & 0.87 & 2.53 & 0.15\\
\addlinespace
\textbf{Education Level} \\
(\textbf{ref: None}) \\
\quad Primary & 1.13 & 0.72 & 1.77 & 0.59\\
\quad Secondary & 0.93 & 0.61 & 1.44 & 0.75\\
\quad Higher & 1.03 & 0.61 & 1.72 & 0.92\\
\addlinespace
\textbf{Place of Residence} \\
(\textbf{ref: Urban}) \\
\quad Rural & 0.39 & 0.28 & 0.53 & <0.01\\
\addlinespace
\textbf{Wealth Index}  \\
(\textbf{ref: Poorest})  \\
\quad Second & 0.74 & 0.54 & 1.02 & 0.07\\
\quad Middle & 0.95 & 0.67 & 1.33 & 0.75\\
\quad Fourth & 1.20 & 0.83 & 1.73 & 0.33\\
\quad Richest & 1.78 & 1.11 & 2.85 & 0.02\\
\addlinespace
$\pmb\sigma^2_{Districts}$ & 0.60 & & \\
\addlinespace
\addlinespace
 & & \textbf{Private} & & \\
\addlinespace
\addlinespace
Intercept & 2.59 & 1.63 & 4.13 & <0.01\\
\addlinespace
\textbf{Education Level} & & & & \\
(\textbf{ref: None}) & & & & \\
\quad Primary & 1.35 & 0.96 & 1.90 & 0.08\\
\quad Secondary & 1.12 & 0.80 & 1.55 & 0.51\\
\quad Higher & 1.23 & 0.83 & 1.82 & 0.3\\
\addlinespace
\textbf{Place of Residence} \\
\textbf{ref: Urban} \\
\quad Rural & 0.52 & 0.40 & 0.68 & <0.01\\
\addlinespace
\textbf{Wealth Index} \\
(\textbf{ref: Poorest}) \\
\quad Second & 0.99 & 0.78 & 1.27 & 0.95\\
\quad Middle & 1.29 & 0.99 & 1.67 & 0.06\\
\quad Fourth & 1.79 & 1.35 & 2.37 & <0.01\\
\quad Richest & 2.94 & 2.05 & 4.20 & <0.01\\
\addlinespace
$\pmb\sigma^2_{Districts}$ & 0.88 & & \\
\bottomrule
\end{tabular}
\end{table}

\newpage

![Distribution of Health Seeking Behavior Over Districts](../multinom-dristrics.pdf)

\newpage

\begin{table}[htbp]
\centering
\caption{Comparison of MOR Between Null Models and Covariate-Adjusted Models}
\label{tab:mord_comparison}
\begin{tabular}{@{}lcccc@{}}
\toprule
 & \multicolumn{2}{c}{\textbf{Null Models\footnote{Null Models: This model does not include any covariates.}}} & \multicolumn{2}{c}{\textbf{Covariate-Adjusted Models}} \\
 \cmidrule(lr){2-3} \cmidrule(lr){4-5}
Term & Estimates & 95\% CI & Estimates & 95\% CI \\ 
\midrule
$\widehat{\mbox{MOR}_{Govt}}$ & 2.18 & (1.80, 2.65) & 2.10 & (1.73, 2.55) \\
$\widehat{\mbox{MOR}_{Private}}$ & 2.55 & (2.10, 3.11) & 2.45 & (2.02, 2.96) \\
\bottomrule
\end{tabular}
\scriptsize
\text{Null Models: This model does not include any covariates}
\end{table}